---
title: "131 hw3"
author: "Tianyi Li"
date: '2022-04-16'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,
                      warning = FALSE)
```

```{r}
library(ggplot2)
library(tidymodels)
library(ISLR)  
library(ISLR2) 
library(discrim)
library(poissonreg)
library(corrr)
library(klaR) 
tidymodels_prefer()
```

```{r}
titanic <- read.csv("titanic.csv")
head(titanic)
titanic$survived<-factor(titanic$survived, levels=c('Yes','No'))
titanic$pclass<-factor(titanic$pclass)
```
Question 1

This dataset can be divided into different subgroups, and stratified sampling can generate representations more accurately of the population.

```{r}
set.seed(1202)
titanic_split<-initial_split(titanic,prop=0.80,
                             strata = survived )
titanic_train<-training(titanic_split)
titanic_test<-testing(titanic_split)
```

Question 2

The number of passengers who survived is significantly more than that of didn't survived.

```{r}
ggplot(titanic_train,aes(x=survived))+geom_bar()
```

Question 3

I see a symmetric and evenly distributed pattern. 
age and sib_sp are negatively correlated, parch and sib_sp are positively correlated.

```{r}
cor_titanic <- titanic_train %>%
  select(is.numeric) %>%
  correlate()
rplot(cor_titanic)
```

Question 4
```{r}
titanic_recipe <- recipe(survived ~ pclass + sex + age + sib_sp + 
                           parch + fare, data = titanic_train) %>% 
  step_impute_linear(age) %>% 
  step_dummy(all_nominal_predictors()) %>% 
  step_interact(terms= ~ starts_with("sex"):fare+
                  age:fare)
titanic_recipe
```

Question 5
```{r}
log_reg <- logistic_reg() %>% 
  set_engine("glm") %>% 
  set_mode("classification")
log_wkflow <- workflow() %>% 
  add_model(log_reg) %>% 
  add_recipe(titanic_recipe)
log_fit <- fit(log_wkflow, titanic_train)
```

Question 6
```{r}
lda_mod <- discrim_linear() %>% 
  set_mode("classification") %>% 
  set_engine("MASS")
lda_wkflow <- workflow() %>% 
  add_model(lda_mod) %>% 
  add_recipe(titanic_recipe)
lda_fit <- fit(lda_wkflow, titanic_train)
```

Question 7
```{r}
qda_mod <- discrim_quad() %>% 
  set_mode("classification") %>% 
  set_engine("MASS")
qda_wkflow <- workflow() %>% 
  add_model(qda_mod) %>% 
  add_recipe(titanic_recipe)
qda_fit <- fit(qda_wkflow, titanic_train)
```

Question 8
```{r}
nb_mod <- naive_Bayes() %>% 
  set_mode("classification") %>% 
  set_engine("klaR") %>% 
  set_args(usekernel = FALSE) 
nb_wkflow <- workflow() %>% 
  add_model(nb_mod) %>% 
  add_recipe(titanic_recipe)
nb_fit <- fit(nb_wkflow, titanic_train)
```

Question 9

Logistic Regression model achieved the highest accuracy.

```{r}
bind_titanic_train=bind_cols(predict(log_fit,new_data=titanic_train,type="class"),
                             predict(lda_fit,new_data=titanic_train,type="class"),
                             predict(qda_fit,new_data=titanic_train,type="class"),
                             predict(nb_fit,new_data=titanic_train,type="class"),
                             titanic_train$survived)
```

```{r}
log_reg_acc <- augment(log_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
log_reg_acc
```
```{r}
lda_acc <- augment(lda_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
lda_acc
```
```{r}
qda_acc <- augment(qda_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
qda_acc
```
```{r}
nb_acc <- augment(nb_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
nb_acc
```
```{r}
accuracies <- c(log_reg_acc$.estimate, lda_acc$.estimate, 
                nb_acc$.estimate, qda_acc$.estimate)
models <- c("Logistic Regression", "LDA", "Naive Bayes", "QDA")
results <- tibble(accuracies = accuracies, models = models)
results %>% 
  arrange(-accuracies)
```

Question 10

The model performs fairly, not very accurately. The value differ because the model is optimized for the training accuracy.

```{r}
predict(log_fit, new_data = titanic_test, type = "prob")
augment(log_fit, new_data = titanic_test) %>%
  conf_mat(truth = survived, estimate = .pred_class) 
```
```{r}
augment(log_fit, new_data = titanic_test) %>%
  roc_curve(survived, .pred_Yes) %>%
  autoplot()
```
```{r}
augment(log_fit, new_data = titanic_test) %>%
  roc_auc(survived,.pred_Yes)
```



